---
title: "Negotiation Behaviours and Attitudes Report"
params:
  name: NA
  df: NA
  planning_items: NA
  bargaining_items: NA
  implementation_items: NA
  nfc_items: NA
  ncs_items: NA
  svo_angle: NA
  svo_type: NA
  svo_items: NA
output:
  pdf_document:
classoption: a4paper
header-includes:
    - \usepackage{fancyhdr}
    - \usepackage[utf8]{inputenc}
geometry: margin = 1in
---

\addtolength{\headheight}{.5cm} 
\pagestyle{fancyplain} 
\lhead{\includegraphics[height=1.7cm]{www/mbslogo.jpg}}
\renewcommand{\headrulewidth}{0pt} 
\let\oldrule=\rule
    \renewcommand{\rule}[1]{\oldrule{\linewidth}} 
\pagenumbering{gobble}

# `r params$name`

This report provides feedback about how you engage in effective negotiation behaviours. It should be a source of reflection on areas where you are performing well, and areas where you can improve. You will also see feedback about three other properties that affect your negotiations: need for closure, need for cognition, and social value orientation. In each section of the report, you can see an explanation of the measure and how you compare with your peers. *Note: "MBS Participants" refers to the average score of MBS participants.*


```{r setup, include=FALSE}
# Load necessary libraries
library(knitr)
library(rmarkdown)
library(tools)
library(openxlsx)
library(dplyr)
library(xtable)
library(grid)
library(ggplot2)
library(ggpubr)
library(stringr)
library(cowplot)
library(tidyr)
options(width = 120)
knitr::opts_chunk$set(comment = NA)

# Prep the datasets
plot_data <- params$df
planning_items <- params$planning_items
bargaining_items <- params$bargaining_items
implementation_items <- params$implementation_items
nfc_items <- params$nfc_items  # Add this line
ncs_items <- params$ncs_items  # Add this line
```

# Planning

The planning aspect of negotiation refers to behaviours that should take place before the first offer is made. 

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
pre_df <- plot_data[9, ]

pre_long <- pre_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

title <- str_pad("Overall planning score", width = 40, side=c('right'), pad=' ')

q11 <- ggplot(pre_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = pre_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q11 <- q11 + rotate()

q11
```

### Planning dimensions

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
title <- str_wrap("Efforts to initiate the negotiation and to understand the situation", width = 40)
title <- unlist(str_split(title, pattern = "\\n", n = Inf, simplify = FALSE), use.names = F)
title <- str_pad(title, width = 40, side = c("right"), pad = " ")
title <- paste(title[1], title[2], sep ="\n")

pre_df <- plot_data[10, ]

pre_long <- pre_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

q1 <- ggplot(pre_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = pre_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q1 <- q1 + rotate()
```

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
title <- str_wrap("Understanding the counterpart's intentions and behaviours", width = 40)
title <- unlist(str_split(title, pattern = "\\n", n = Inf, simplify = FALSE), use.names = F)
title <- str_pad(title, width = 40, side = c("right"), pad = " ")
title <- paste(title[1], title[2], sep ="\n")

pre_df <- plot_data[11, ]

pre_long <- pre_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

q2 <- ggplot(pre_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = pre_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q2 <- q2 + rotate()
```

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
title <- str_wrap("Efforts to understand your needs and interests for the negotiation", width = 40)
title <- unlist(str_split(title, pattern = "\\n", n = Inf, simplify = FALSE), use.names = F)
title <- str_pad(title, width = 40, side = c("right"), pad = " ")
title <- paste(title[1], title[2], sep ="\n")

pre_df <- plot_data[13, ]

pre_long <- pre_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

q3 <- ggplot(pre_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = pre_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q3 <- q3 + rotate()
```

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
title <- str_wrap("Awareness of what will happen if the negotiation fails", width = 40)
title <- unlist(str_split(title, pattern = "\\n", n = Inf, simplify = FALSE), use.names = F)
title <- str_pad(title, width = 40, side = c("right"), pad = " ")
title <- paste(title[1], title[2], sep ="\n")

pre_df <- plot_data[12, ]

pre_long <- pre_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

q4 <- ggplot(pre_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = pre_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q4 <- q4 + rotate()

pl <- align_plots(q1, q2, q3, q4, align="v")

ggdraw(pl[[1]])
ggdraw(pl[[2]])
ggdraw(pl[[3]])
ggdraw(pl[[4]])
```

\newpage

# Need for Closure Assessment

This section shows your responses to the Need for Closure scale, which measures your preference for order, structure, and closure in your thinking and decision-making. It is common to have somewhat high need for closure, but if your score is very high, that might indicate that you face challenges remaining open and keeping negotiations going long enough to maximise value creation---or coming back to re-discuss issues that had been tentatively decided.

## Your Need for Closure Profile

```{r nfc_chart, echo=FALSE, fig.width=8, fig.height=5, fig.align='center'}
# Create a dataframe for NFC categories
nfc_df <- plot_data %>% 
  filter(Category %in% c("nfc_order", "nfc_predictability", "nfc_decisiveness", 
                         "nfc_ambiguity", "nfc_closemindedness", "nfc_total"))

# Skip this chunk if no NFC data is available
if(nrow(nfc_df) > 0) {
  # Rename categories for better readability
  nfc_df$Category_Label <- factor(nfc_df$Category, 
                                 levels = c("nfc_order", "nfc_predictability", "nfc_decisiveness", 
                                            "nfc_ambiguity", "nfc_closemindedness", "nfc_total"),
                                 labels = c("Preference for Order", "Preference for Predictability", 
                                            "Decisiveness", "Discomfort with Ambiguity", 
                                            "Close-mindedness", "Overall Need for Closure"))
  
  # Create the chart
  ggplot(nfc_df, aes(x = Category_Label)) +
    geom_bar(aes(y = Your_Response, fill = "Your Score"), stat = "identity", position = "dodge", width = 0.4) +
    geom_point(aes(y = Benchmark, color = "Benchmark"), size = 3) +
    geom_line(aes(y = Benchmark, group = 1, color = "Benchmark"), linetype = "dashed", size = 1) +
    scale_fill_manual(values = c("Your Score" = "#4285F4")) +
    scale_color_manual(values = c("Benchmark" = "#EA4335")) +
    labs(title = "Your Need for Closure Profile",
         y = "Score (1-6 scale)",
         x = "") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.title = element_blank(),
          legend.position = "bottom")
}
```

## Interpretation

```{r nfc_interpret, echo=FALSE, results='asis'}
# Skip this chunk if no NFC data is available
if(exists("nfc_df") && nrow(nfc_df) > 0) {
  cat("- **Preference for Order** (Score: ", round(nfc_df$Your_Response[nfc_df$Category == "nfc_order"], 2), "): Your preference for order, structure, and routine in your life.\n\n")
  
  cat("- **Preference for Predictability** (Score: ", round(nfc_df$Your_Response[nfc_df$Category == "nfc_predictability"], 2), "): Your comfort with predictable situations and discomfort with uncertainty.\n\n")
  
  cat("- **Decisiveness** (Score: ", round(nfc_df$Your_Response[nfc_df$Category == "nfc_decisiveness"], 2), "): Your tendency to make quick decisions to achieve closure.\n\n")
  
  cat("- **Discomfort with Ambiguity** (Score: ", round(nfc_df$Your_Response[nfc_df$Category == "nfc_ambiguity"], 2), "): Your level of discomfort with ambiguous or uncertain situations.\n\n")
  
  cat("- **Close-mindedness** (Score: ", round(nfc_df$Your_Response[nfc_df$Category == "nfc_closemindedness"], 2), "): Your openness to considering different opinions or perspectives.\n\n")
  
  cat("- **Overall Need for Closure** (Score: ", round(nfc_df$Your_Response[nfc_df$Category == "nfc_total"], 2), "): Your general tendency to seek definitive answers and avoid ambiguity.\n\n")
}
```

### How This Relates to Negotiation

Your Need for Closure can influence your negotiation style in several ways:

- Higher scores may indicate a preference for reaching agreements quickly, potentially at the expense of exploring all options.
- Lower scores may indicate comfort with ambiguity and willingness to keep options open longer during negotiations.
- Understanding your need for closure can help you recognise when you might be rushing to resolution versus when you might benefit from exploring more options.

\newpage

# Need for Cognition Assessment

This section shows your responses to the Need for Cognition scale, which measures your tendency to engage in and enjoy thinking.

## Your Need for Cognition Score

```{r ncs_chart, echo=FALSE, fig.width=6, fig.height=4, fig.align='center'}
# Create a dataframe for NCS category
ncs_df <- plot_data %>% 
  filter(Category %in% c("ncs_total"))

# Skip this chunk if no NCS data is available
if(nrow(ncs_df) > 0) {
  # Rename category for better readability
  ncs_df$Category_Label <- "Need for Cognition"
  
  # Create the chart
  ggplot(ncs_df, aes(x = Category_Label)) +
    geom_bar(aes(y = Your_Response, fill = "Your Score"), stat = "identity", width = 0.5) +
    geom_point(aes(y = Benchmark, color = "Average Score"), size = 3) +
    scale_fill_manual(values = c("Your Score" = "#4285F4")) +
    scale_color_manual(values = c("Average Score" = "#EA4335")) +
    ylim(0, 5) +
    labs(title = "Your Need for Cognition Score",
         y = "Score (1-5 scale)",
         x = "") +
    theme_minimal() +
    theme(legend.title = element_blank(),
          legend.position = "bottom")
}
```

## Interpretation

```{r ncs_interpret, echo=FALSE, results='asis'}
# Skip this chunk if no NCS data is available
if(exists("ncs_df") && nrow(ncs_df) > 0) {
  cat("Your Need for Cognition score (", round(ncs_df$Your_Response[1], 2), ") reflects your tendency to engage in and enjoy thinking.\n\n")
  
  cat("- **Higher scores** (above 3.5) suggest that you tend to enjoy cognitive challenges and complex problem-solving. You likely prefer to think deeply about issues and are motivated by intellectual engagement.\n\n")
  
  cat("- **Lower scores** (below 3.5) suggest that you may prefer simpler cognitive tasks and might be less inclined to engage in effortful thinking when it's not necessary.\n\n")
}
```

### How This Relates to Negotiation

Your Need for Cognition can influence your negotiation approach in several ways:

- A higher Need for Cognition may lead you to analyse negotiation situations more thoroughly, consider more alternatives, and develop more complex negotiation strategies.

- You might enjoy the intellectual challenge of negotiation, including analysing the other party's interests, crafting persuasive arguments, and finding creative solutions that satisfy both parties.

- Understanding your Need for Cognition can help you recognise when you might benefit from more or less cognitive engagement in negotiations, depending on the situation.

### Planning behaviours for reflection

```{r, tidy = T, echo = F}
dypre <- planning_items

dypre <- subset(dypre, Item != "Plan20" & Item != "Plan21")

dypre$q <- c("Spend time thinking about your counterpart's goals.",
             "Spend time studying your counterpart's tactics and patterns of behaviour in similar situations.",
             "Spend time studying the counterpart's emotional state as they enter into negotiations.",
             "Spend time researching whether your counterpart might value things differently than you.",
             "Spend time researching the counterpart's point of view on the situation.",
             "Exhaust every source of information at your disposal (including, but not limited to, family, friends, co-workers, institutions, the library, and the Internet).",
             "Research alternative outcomes that satisfy the need of the parties (i.e., find alternative arrangements that meet your and your counterpart's needs).",
             "Communicate in advance your intention to negotiate.",
             "Make sure all relevant parties will be included in the negotiation.",
             "Establish a shared perception of the situation that requires resolution.",
             "Attempt to remove or minimise distractions that could draw attention away from the negotiation.",
             "Spend time researching the events leading to the negotiation.",
             "Spend time thinking about your goals.",
             "Prioritise the goals for the negotiation.",
             "Create a table or list of what you value most to what you value least.",
             "Ensure that you have the necessary resources to follow through with the deal that you reach.",
             "Maintain competence in the skills needed to analyse the deal (e.g., technical evaluation, accounting, developing relationships, etc.).",
             "Understand your no-deal options.",
             "Understand your counterpart's no-deal options.")

dypre$c_value <- c(5.02, 4.02, 4.19, 4.08, 4.59,
                   4.22, 4.9, 4.59, 5.03, 5,
                   4.25, 4.34, 6.03, 5.5, 4.1,
                   5, 4.9, 4.86, 3.94)

dypre$Dimension <- c("Understanding the counterpart",
             "Understanding the counterpart",
             "Understanding the counterpart",
             "Understanding the counterpart",
             "Understanding the counterpart",
             "Setting the arena",
             "Setting the arena",
             "Setting the arena",
             "Setting the arena",
             "Setting the arena",
             "Setting the arena",
             "Setting the arena",
             "Preparing the self",
             "Preparing the self",
             "Preparing the self",
             "Preparing the self",
             "Preparing the self",
             "Understanding the impasse",
             "Understanding the impasse")

dypre <- dypre[, c(5, 3, 2, 4)]

colnames(dypre) <- c("Dimension", "Behaviour", "You", "MBS Participants")

dypre <- dypre[order(dypre$You, decreasing = TRUE), ]

```


```{r, results = 'asis', echo = F}
writeLines("\\begin{flushleft}")
cat("For further reflection, below are the three questions you rated highest:")
writeLines("\\end{flushleft}")
```
```{r, echo = F}
kable(dypre[1:3, ], row.names	= F)
```
```{r, results = 'asis', echo = F}
writeLines("\\begin{flushleft}")
cat("For further reflection, below are the three questions you rated lowest:")
writeLines("\\end{flushleft}")
```
```{r, echo = F}
kable(dypre[17:19, ],  row.names	= F)
```

\newpage

# Social Value Orientation (SVO)

Social Value Orientation (SVO) describes how people value outcomes for themselves and others in interdependent situations. Your SVO profile indicates your preferences for allocating resources between yourself and others.

## Your SVO Results

```{r svo_chart, echo=FALSE, fig.width=7, fig.height=4, fig.align='center'}
# Check if SVO angle exists in the data
if(exists("params") && !is.null(params$svo_angle) && !is.na(params$svo_angle)) {
  # Create angle visualization
  angle_rad <- params$svo_angle * pi / 180
  x_end <- cos(angle_rad)
  y_end <- sin(angle_rad)
  
  # Create the circular plot
  ggplot() + 
    # Add the circle
    stat_function(fun = function(x) sqrt(1 - x^2), geom = "line", n = 500, 
                  xlim = c(-1, 1), color = "gray60") +
    stat_function(fun = function(x) -sqrt(1 - x^2), geom = "line", n = 500, 
                  xlim = c(-1, 1), color = "gray60") +
    # Add reference lines for the orientation types
    geom_segment(aes(x = 0, y = 0, xend = 1, yend = 0), 
                 linetype = "dashed", color = "gray70") +
    geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1), 
                 linetype = "dashed", color = "gray70") +
    geom_segment(aes(x = 0, y = 0, xend = 0, yend = 1), 
                 linetype = "dashed", color = "gray70") +
    # Add the SVO angle line
    geom_segment(aes(x = 0, y = 0, xend = x_end, yend = y_end), 
                 arrow = arrow(length = unit(0.3, "cm")), color = "#007bff", size = 1.2) +
    # Add the labels for the orientations
    annotate("text", x = 0, y = 1.1, label = "Altruistic", color = "gray40") +
    annotate("text", x = 0.8, y = 0.8, label = "Prosocial", color = "gray40") +
    annotate("text", x = 1.1, y = 0, label = "Individualistic", color = "gray40") +
    annotate("text", x = 0.8, y = -0.8, label = "Competitive", color = "gray40") +
    # Add angle label
    annotate("text", x = x_end/2 - 0.1, y = y_end/2 + 0.1, 
             label = paste0(round(params$svo_angle, 1), "°"), 
             color = "#007bff", fontface = "bold") +
    # Set the plot appearance
    coord_fixed(ratio = 1, xlim = c(-1.2, 1.2), ylim = c(-1.2, 1.2)) +
    theme_minimal() +
    theme(axis.text = element_blank(),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          panel.grid = element_blank(),
          plot.title = element_text(hjust = 0.5)) +
    ggtitle("Your Social Value Orientation")
} else {
  # Show a message if SVO data is missing
  grid::grid.text("SVO data not available", gp = grid::gpar(fontsize = 14, col = "gray50"))
}
```

```{r svo_type_display, echo=FALSE, results='asis'}
if(exists("params") && !is.null(params$svo_type) && !is.na(params$svo_type)) {
  cat("**Your SVO angle:** ", round(params$svo_angle, 2), "°\n\n")
  cat("**Your SVO type:** ", params$svo_type, "\n\n")
}
```

## What Your SVO Type Means

```{r svo_interpretation, echo=FALSE, results='asis'}
if(exists("params") && !is.null(params$svo_type)) {
  cat("Based on your responses, your Social Value Orientation is classified as **", params$svo_type, "**. This means:\n\n")
  
  if(params$svo_type == "Competitive") {
    cat("You tend to maximise your own outcomes relative to others, potentially seeking advantage over others even at a cost to joint outcomes. In negotiations, this may appear as a win-lose approach.")
  } else if(params$svo_type == "Individualistic") {
    cat("You tend to maximise your own outcomes without strong regard for others' outcomes. In negotiations, this often appears as a focus on claiming value for yourself.")
  } else if(params$svo_type == "Prosocial") {
    cat("You tend to maximise joint outcomes and equality in distributions. In negotiations, this often appears as a focus on creating value and finding win-win solutions.")
  } else if(params$svo_type == "Altruistic") {
    cat("You tend to prioritise others' outcomes over your own. In negotiations, this might appear as an emphasis on the counterpart's needs and interests.")
  } else {
    cat("Your responses resulted in an unclassified orientation. This sometimes happens when responses fall on the boundary between categories.")
  }
}
```

## SVO and Negotiation

Your Social Value Orientation has important implications for how you approach negotiations:

- **Competitive** orientations may focus strongly on winning and gaining advantage over others.
- **Individualistic** orientations may focus on maximising personal gain without much concern for the counterpart.
- **Prosocial** orientations tend to look for mutually beneficial outcomes and fair distributions.
- **Altruistic** orientations may prioritise the counterpart's needs, sometimes at personal cost.

Understanding your own orientation can help you recognise when your natural tendencies might help or hinder different types of negotiations. For instance, prosocial orientations may excel in long-term relationship building, while individualistic orientations might serve better in one-time distributive bargaining.

```{r svo_benchmark, echo=FALSE, fig.width=7, fig.height=3, fig.align='center'}
# Create benchmark comparison if data exists
if(exists("plot_data") && "SVO_angle" %in% plot_data$Category) {
  # Extract SVO angle data
  svo_df <- plot_data %>% 
    filter(Category == "SVO_angle")
  
  # Create the benchmark comparison
  benchmark <- svo_df$Benchmark[1]
  user_svo <- svo_df$Your_Response[1]
  
  # Create the plot with category boundaries
  ggplot() +
    # Add category background colors
    geom_rect(aes(xmin = -90, xmax = -12.04, ymin = 0, ymax = 1), fill = "#f8f9fa", alpha = 0.5) +
    geom_rect(aes(xmin = -12.04, xmax = 22.45, ymin = 0, ymax = 1), fill = "#e9ecef", alpha = 0.5) +
    geom_rect(aes(xmin = 22.45, xmax = 57.15, ymin = 0, ymax = 1), fill = "#f8f9fa", alpha = 0.5) +
    geom_rect(aes(xmin = 57.15, xmax = 90, ymin = 0, ymax = 1), fill = "#e9ecef", alpha = 0.5) +
    # Add category labels
    annotate("text", x = -51, y = 0.5, label = "Competitive", color = "gray40") +
    annotate("text", x = 5, y = 0.5, label = "Individualistic", color = "gray40") +
    annotate("text", x = 40, y = 0.5, label = "Prosocial", color = "gray40") +
    annotate("text", x = 73.5, y = 0.5, label = "Altruistic", color = "gray40") +
    # Add the benchmark line
    geom_vline(xintercept = benchmark, color = "gray60", linetype = "dashed", size = 1) +
    annotate("text", x = benchmark, y = 0.85, label = "Benchmark", color = "gray60") +
    # Add the user's score
    geom_vline(xintercept = user_svo, color = "#007bff", size = 1.2) +
    annotate("text", x = user_svo, y = 0.15, label = "Your Score", color = "#007bff", fontface = "bold") +
    # Set the plot appearance
    scale_x_continuous(limits = c(-90, 90), breaks = c(-90, -45, 0, 45, 90)) +
    scale_y_continuous(limits = c(0, 1)) +
    theme_minimal() +
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y = element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.minor = element_blank()) +
    labs(x = "SVO Angle (degrees)", title = "Your SVO Compared to Benchmarks")
}
```

Most people (approximately 60%) are classified as prosocial, while about 30% are individualistic, 5% competitive, and 5% altruistic. Your position relative to these distributions can help you understand your natural tendencies compared to others.

\newpage

# Bargaining

The bargaining aspect of negotiation refers to the process of making offers and proposals. 

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
title <- str_pad("Overall bargaining score", width = 40, side=c('right'), pad=' ')

barg_df <- plot_data[1, ]

barg_long <- barg_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

q5 <- ggplot(barg_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = barg_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q5 <- q5 + rotate()

q5
```

## Bargaining dimensions

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
title <- str_wrap("Constructing and communicating persuasive arguments", width = 40)
title <- unlist(str_split(title, pattern = "\\n", n = Inf, simplify = FALSE), use.names = F)
title <- str_pad(title, width = 40, side = c("right"), pad = " ")
title <- paste(title[1], title[2], sep ="\n")

barg_df <- plot_data[2, ]

barg_long <- barg_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

q6 <- ggplot(barg_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = barg_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q6 <- q6 + rotate()
```

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
title <- str_wrap("Making a deal that includes all of your interests", width = 40)
title <- unlist(str_split(title, pattern = "\\n", n = Inf, simplify = FALSE), use.names = F)
title <- str_pad(title, width = 40, side = c("right"), pad = " ")
title <- paste(title[1], title[2], sep ="\n")

barg_df <- plot_data[3, ]

barg_long <- barg_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

q7 <- ggplot(barg_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = barg_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q7 <- q7 + rotate()
```

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
title <- str_wrap("Efforts to claim as much value as possible", width = 40)
title <- unlist(str_split(title, pattern = "\\n", n = Inf, simplify = FALSE), use.names = F)
title <- str_pad(title, width = 40, side = c("right"), pad = " ")
title <- paste(title[1], title[2], sep ="\n")

barg_df <- plot_data[4, ]

barg_long <- barg_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

q8 <- ggplot(barg_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = barg_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q8 <- q8 + rotate()
```

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
title <- str_wrap("Efforts to make both sides better off", width = 40)
title <- unlist(str_split(title, pattern = "\\n", n = Inf, simplify = FALSE), use.names = F)
title <- str_pad(title, width = 40, side = c("right"), pad = " ")
# title <- paste(title[1], title[2], sep ="\n")

barg_df <- plot_data[5, ]

barg_long <- barg_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

q9 <- ggplot(barg_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = barg_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q9 <- q9 + rotate()

bl <- align_plots(q6, q7, q8, q9, align="v")

ggdraw(bl[[1]])
ggdraw(bl[[2]])
ggdraw(bl[[3]])
ggdraw(bl[[4]])
```

\newpage

## Bargaining behaviours for reflection

```{r, tidy = T, echo = F}
dybar <- bargaining_items

dybar <- subset(dybar, Item != "Barg10")

dybar <- dybar[1:25, ]
 
dybar$q <- c("Have plans in advance to deal with counterproductive (e.g., negative, extreme, irrational) behaviour from your counterpart.",
"Ask questions to learn about your counterpart.",
"Test your understanding of what your counterpart was trying to say by repeating what they said.",
"Try to focus on satisfying your underlying needs rather than a specific list of requirements.",
"Spend time inventing options for mutual benefit.",
"Keep track of how much value is created by systematically evaluating each offer against previous offers.",
"Try to reach a deal that touches on all of the issues involved.",
"Review the final terms with your counterpart to confirm mutual agreement about their interpretation.",
"Make sure that you were fully understood.",
"Check whether your arguments are persuasive.",
"Check whether your counterpart is telling the truth.",
"Check whether the counterpart is committed to making a deal with you.",
"Make sure the help you are getting is appropriate for the task at hand.",
"Justify each offer with a reason.",
"Provide reasons that the counterpart should find plausible.",
"Present facts that support your offer.",
"Support your offer with facts.",
"Refuse to make concessions.",
"Insist on getting something every time you make a concession.",
"Ask for a lot in your offers.",
"Avoid making concessions.",
"Use your power to make the counterpart concede",
"Always try to get something in return for an accommodation you make",
"Make ambitious offers.",
"Downplay threats made by the counterpart")

dybar$c_value <- c(4.21, 5.18, 4.74, 4.55, 5.21,
                   4.15, 5.05, 5.35, 5.51, 4.71,
                   4.83, 4.71, 4.87, 5.29, 5.59,
                   5.65, 5.57, 3, 3.4, 3.68,
                   3.29, 3.67, 3.98, 4.05, 3.98)

dybar$Dimension <- c("Working for mutual benefit",
"Working for mutual benefit",
"Working for mutual benefit",
"Working for mutual benefit",
"Working for mutual benefit",
"Working for mutual benefit",
"Comprehensive",
"Comprehensive",
"Comprehensive",
"Argumentation",
"Argumentation",
"Argumentation",
"Argumentation",
"Argumentation",
"Argumentation",
"Argumentation",
"Argumentation",
"Getting the most",
"Getting the most",
"Getting the most",
"Getting the most",
"Getting the most",
"Getting the most",
"Getting the most",
"Getting the most")

dybar <- dybar[, c(5, 3, 2, 4)]

colnames(dybar) <- c("Dimension", "Behaviour", "You", "MBS Participants")

dybar <- dybar[order(dybar$You, decreasing = TRUE), ]
```

```{r, results = 'asis', echo = F}
writeLines("\\begin{flushleft}")
cat("For further reflection, below are the three questions you rated highest:")
writeLines("\\end{flushleft}")
```
```{r, echo = F}
kable(dybar[1:3, ], row.names	= F)
```
```{r, results = 'asis', echo = F}
writeLines("\\begin{flushleft}")
cat("For further reflection, below are the three questions you rated lowest:")
writeLines("\\end{flushleft}")
```
```{r, echo = F}
kable(dybar[23:25, ],  row.names	= F)
```

\newpage

# Implementation

The implementation aspect of negotiation refer to actions that should be taken after reaching an agreement. 

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
title <- str_pad("Overall implementation score", width = 40, side=c('right'), pad=' ')

imp_df <- plot_data[6, ]

imp_long <- imp_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

q10 <- q10 + rotate()

q10
```

## Implementation dimensions

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
title <- str_wrap("Efforts that help you and your counterpart to follow through on promises", width = 40)
title <- unlist(str_split(title, pattern = "\\n", n = Inf, simplify = FALSE), use.names = F)
title <- str_pad(title, width = 40, side = c("right"), pad = " ")
title <- paste(title[1], title[2], sep ="\n")

imp_df <- plot_data[8, ]

imp_long <- imp_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

q11 <- ggplot(imp_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = imp_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q11 <- q11 + rotate()

```

```{r, echo = F, fig.align='center', fig.width = 6.4, fig.height = 1, include = T, message = F, fig.margin = T, warning = F, results = 'asis'}
title <- str_wrap("Consulting more experienced negotiators to improve for the future", width = 40)
title <- unlist(str_split(title, pattern = "\\n", n = Inf, simplify = FALSE), use.names = F)
title <- str_pad(title, width = 40, side = c("right"), pad = " ")
title <- paste(title[1], title[2], sep ="\n")

imp_df <- plot_data[7, ]

imp_long <- imp_df %>%
  pivot_longer(cols = c(Your_Response, Benchmark),
               names_to = "Measure",
               values_to = "Value")

q12 <- ggplot(imp_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = imp_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q12 <- q12 + rotate()

il <- align_plots(q11, q12, align="v")

ggdraw(il[[1]])
ggdraw(il[[2]])
```

## Items for reflection

```{r, tidy = T, echo = F, results = 'asis'}
dyimp <- implementation_items

imp_subset <- c("Post1", "Post2", "Post3", "Post5", "Post6")

dyimp <- subset(dyimp, Item %in% imp_subset)

dyimp$q <- c("Express your commitment to the agreement.", 
"Check that you have addressed your counterpart's key concerns.",
"Agree on a plan to implement every aspect of the agreement.",
"Periodically seek advice about negotiating from a more experienced negotiator.",
"Periodically seek advice about negotiating from peers.")

dyimp$Dimension <- c("Implementation",
"Implementation",
"Implementation",
"Seeking feedback",
"Seeking feedback")

dyimp$c_value <- c(5.48, 4.97, 5.25, 4.1, 4.22)

dyimp <- dyimp[, c(4, 3, 2, 5)]

colnames(dyimp) <- c("Dimension", "Behaviour", "You", "MBS Participants")

dyimp <- dyimp[order(dyimp$You, decreasing = TRUE), ]
```


```{r, results = 'asis', echo = F}
writeLines("\\begin{flushleft}")
cat("For further reflection, below are the two questions you rated highest:")
writeLines("\\end{flushleft}")
```
```{r, echo = F}
kable(dyimp[1:2, ], row.names = F)
```
```{r, results = 'asis', echo = F}
writeLines("\\begin{flushleft}")
cat("For further reflection, below are the two questions you rated lowest:")
writeLines("\\end{flushleft}")
```
```{r, echo = F}
kable(dyimp[4:5, ], row.names = F)
```

\newpage <- ggplot(imp_long, aes(y = Value, x = Measure, fill = factor(Measure))) +
  geom_bar(stat = "identity") + theme_bw() + ylab("") + xlab(title) +
  theme(legend.position = "none", axis.title.y = element_text(angle=0, hjust = 0, size = 9)) + 
  geom_text(data = imp_long, aes(label = round(Value, 2), y = 6.5)) +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7), 
  labels=c("1" = "1", "2" = "", "3" = "3", "4" = "", "5" = "5", "6" = "", "7" = "7")) + 
  scale_x_discrete(labels = c("Your_Response" = "You", "Benchmark" = "MBS Participants")) + 
  coord_cartesian(ylim=c(1,8)) + scale_fill_manual(values = c("grey60", "Green")) 
q10
